\tool

### 2017-11-14 paper/paper.tex
Updates to Tool section of paper

\section{Tool}
Our approach, \tool, aims to increase awareness of useful programming tools to software engineers. This section describes the design and implementation of our system.

\subsection{Design}
Previous research shows that recommendations between peers is an effective way to increase tool discovery and adoption~\cite{Murphy-HillPeerInteraction}. Many automated help systems are designed to simulate user-to-user recommendations in order to increase awareness of application tools and features, for instance Microsoft's intelligent office assistant Clippy. To better understand what makes peer interactions an effective mode of tool discovery, our prior work observed how colleagues recommend tools to each other while working on tasks. We found that \emph{receptiveness} has a significant outcome of a tool recommendation, while other interaction characteristics such as politeness or persuasiveness did no impact effectivenesst~\cite{vlhcc17}.

@@

Previous work emphasizes the importance of receptivity. Fogg outlined best practicies for creating persuasive technology to change user behavior, and argued designers must choose a receptive audience~\cite{FoggPersuasive}. He defines receptiveness using two criteria: 1) demonstrating a desire to adopt the target behavior and 2) familiarity with the technology. Below we present how \tool~integrates each of these concepts and how they influence the design of the system.

@@

Software has permeated every area of our society. The primary desire of software users is to have enjoyable and problem-free experiences with software. The developers of these applications also have similar desires, to create high-quality and functioning programs for users. A 2002 study by the National Institute of Standards and Technology revealed that software engineers demonstrate this desire by spending the majority of the software development process and 70-80\% of their time testing and debugging code~\cite{NIST}. To aid developers in finding, fixing, and preventing various issues in code, many different types of tools have been created to help save time and effort in completing these tasks. We aim to increase awareness of these tools and improve software developer productivity by automatically making recommendations to capitalize on user and programmer desires to have mistake-free software.

To target this desire, our initial implementation automatically recommends \textsc{Error Prone}, a static analysis tool created by Google to check for errors in Java code based on a suite of bug patterns.\footnote{http://errorprone.info} Static analysis tools can improve software quality by automatically inspecting code without running the program. These tools are useful in debugging and creating desireable applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.

@@

Choosing an audience familiar with the target behavior is also vital to increasing adoption. To increase use of helpful programming tools, such as static analysis tools, our system focuses on making recommendations to software engineers in the projects they develop. Familiarity with source code is important for creating software applications, and code understandability is crucial for software development,  maintenance, debugging, and testing~\cite{ASE}.

To choose a familiar audience, we make recommendations to developers of Java projects hosted on Github\footnote{https://github.com}, a popular source code management website that hosts millions of projects and serves millions of users. \tool~makes tool recommendations on pull requests, or proposed changes by contributors submitted to the source code. Developers making these changes should be knowledgeable about the project they are contributing to. Furthermore, our approach makes suggestions for tools when errors are fixed by the developer instead of reporting errors in their changes since pull request creators are familiar with the changes they are proposing to make to the source code. The GitHub interface allows users to review and comment on pull requests in situ with the proposed changes, and this is where we make our recommendations.

@@

\tool~builds on four key concepts to automatically recommend tools to users and improve tool discovery based on our design goals for receptivity.

@@

After analyzing the base and head versions of the code, our approach parses the build output of each version to determine if any reported errors were fixed in the pull request. \textsc{Error Prone} identifies the faults and we developed an algorithm to use that information and determine if a fix to the identified bug was made. \tool~uses the code differencing tool GumTree to identify actions (addition, delete, insert, move, and update) performed to changed files in pull request versions and convert the code into symtax trees~\cite{GumTree}.

@@

Code reviews from developers are often required for examining code changes~\cite{?}. On Github, code reviews are primarily done through pull request comments~\cite{?}. Our approach simulates peer reviews by making recommendations for static analysis tools as a comment to the pull request. Github provides functionality for making comments at specific lines of code in a pull request, and \tool~recommends \textsc{Error Prone} as a comment at the fix location line from the previous step. Additionally, our system also aims to make recommendations using language similar to interactions between colleagues, such as complementing their work using ``Good job!''~\cite{?}.

>>>>

\section{Tool}
Our approach to improving tool discovery, \tool, aims to increase awareness and use of programming tools among software developers. This section describes the design and implementation of our system.

\subsection{Design}
Previous research shows that recommendations between peers is an effective way to increase tool discovery and adoption~\cite{Murphy-HillPeerInteraction}. Many automated help systems are designed to simulate user-to-user recommendations in order to increase awareness of application tools and features, for instance Microsoft's intelligent office assistant Clippy\cite{Clippy}.

To better understand what makes peer interactions an effective mode of tool discovery, our prior work observed how colleagues recommend tools to each other while working on tasks. Our results found that \emph{receptiveness} is a significant factor in determining the effectiveness of a tool recommendation, while other characteristics, such as politeness and persuasiveness, do not significantly impact the outcome~\cite{vlhcc17}. We designed \tool~to integrate user receptivity into our approach for making tool recommendations to increase awareness of programming tools.

@@

Previous work emphasizes the importance of receptivity. Fogg outlined best practicies for creating persuasive technology to change user behavior, and argued designers must choose a receptive audience~\cite{FoggPersuasive}. Our prior work defined receptiveness using two criteria introduced by Fogg: 1) demonstrating a desire and 2) familiarity with the target behavior and technology. Below we explain how \tool~was designed to recommend programming tools to software developers based on their desire and familiarity.

@@

The primary desire of software users is to have enjoyable and problem-free experiences with software. Developers of these applications also have similar desires, to create high-quality and functioning programs for users. A 2002 study revealed that software engineers demonstrate this desire by spending the majority of the software development process and 70-80\% of their time testing and debugging code~\cite{NIST}. To aid developers in finding, fixing, and preventing various issues in code, many different types of tools have been created to help accomplish these tasks. However, despite the existence of effective tools for detecting errors, the number of bugs in software is increasing~\cite{HaveThingsChanged}. We aim to increase awareness of these tools to improve software quality and developer productivity, ultimately meeting users' and developers' desire for less buggy software.

To target this desire of mistake-free code, our initial implementation of \tool~automatically recommends \textsc{Error Prone}.\footnote{http://errorprone.info} \textsc{Error Prone} is a static analysis tool created by Google to check for errors in Java code based on a suite of bug patterns. Static analysis tools can improve software quality by automatically inspecting code without running the program. These tools are useful in debugging and creating desireable applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.

@@

Choosing an audience familiar with the target behavior is also vital to increasing adoption. To increase use of helpful programming tools, such as static analysis tools, our system focuses on making recommendations to software engineers within the context of the projects they develop. Familiarity with source code is important for creating software applications, and code understandability is one of the most important factors for software development, maintenance, debugging, and testing~\cite{Understandability}.

To choose a familiar audience, our approach makes recommendations on Github\footnote{https://github.com}, a popular source code management and version control website that hosts millions of projects and serves millions of users. \tool~makes its recommendations on pull requests, or proposed changes to source code submitted by programmers. Developers making these changes should be knowledgeable about the changes they propose as well as the code base to which they are contributing. Our approach suggests \textsc{Error Prone} when reported errors are fixed by developers in pull requests to capitalize on their familiarity with their modifications. The GitHub interface allows users to review and comment on pull requests in situ with the proposed changes, and this is where we make our recommendations.

@@

\tool~builds on four key concepts to automatically recommend tools to users and improve tool discovery based on our design goals for targeting developer receptivity.

@@

After analyzing the base and head versions of the code, our approach parses the build output of each version to determine if any reported errors were fixed in the pull request. \textsc{Error Prone} identifies faults found in the source code, and we developed an algorithm using that information to determine if changes made to the code in the head version fix the identified bug. Our technique uses the code differencing tool GumTree~\cite{GumTree} to identify actions (addition, delete, insert, move, and update) performed between pull request versions and parse the code to convert the text into abstract syntax trees.

@@

Code reviews from co-workers are often standard practice in software development. Pull requests are the primary method of code contributions and code reviews on Github~\cite{PullRequestReview}. Our approach simulates peer reviews by making recommendations for static analysis tools as a comment to the pull request. Github provides functionality for making comments at specific lines of code in a pull request, and \tool~recommends \textsc{Error Prone} as a comment at the fix location line from the previous step. Additionally, our system  uses language similar to comments between co-workers in recommendations, such as using ``Good job!'' to compliment developers on their work'~\cite{?}.
